Soling at the 2000 Summer Olympics

### 2020-07-22 inst/soling.Rmd
work
fixes #46

  \url{https://en.wikipedia.org/w/index.php?title=Sailing_at_the_2000_Summer_Olympics_\%E2\%80\%93_Soling&oldid=945362535}

@@

>>>>

[https://en.wikipedia.org/w/index.php?title=Sailing_at_the_2000_Summer_Olympics_\%E2\%80\%93_Soling&oldid=945362535]

@@

So `H2` is the _difference_ between `H`--- which is `soling2000` plus
the observations from the roundrobins and quarter finals---and
`soling2000`.  In other words, `H2` is the simply the information in
the roundrobins and quarter finals.

```{r,testH2equalp}
equalp.test(H2)
```
